\documentclass[12pt,a4paper,english]{article}

\usepackage[utf8]{inputenc}

\usepackage{a4}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}

\begin{document}

Dear Sir/Madam,\\

A former colleague of mine, Mara Houston, mentioned that you may be looking for a software developer. With that in mind I have the following to say about myself and the sort of company I would be excited to work for.

I am interested in solving problems. I really enjoy programming. I am interested in learning new things. I get a lot of satisfaction from helping others.

I would like to work in an environment where there is close colaboration between software developers and the stakeholders (and users, where possible). I would like to understand the risks, challenges and opportunities facing the business so that I can ensure the software being, made or changed, delivers value.

I believe that iterative development and short feedback loops are an effective way to ensure that we deliver value; the sooner working software is front of users, the sooner we know we've created the right software and can continue to make it better.

On a technical level, I am interested in having the support of a `continuous integration' server; automated tests; and a rapid and automated deployment pipeline. This allow rapid feedback and makes the decision to ``deploy to production'', for example, a business decision rather than a technical constraint.

On a sentimental level, I want to build software that people love to use.

Of-course, there is more to my life than work.
When I am not programming (and am awake) I can be found swing dancing, rock-climbing, cycling, running, juggling, fire twirling, playing boardgames, enjoying music, drinking coffee, gardening, or reading a book.

I can be contacted at career@roycetownsend.com or on 0405 018 016. I look forward to hearing from you.
\\

Warmest regards,\\
Royce Townsend

\end{document}
