% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}

%c C sharp
\def\Csharp{%
    C\raise.60ex\hbox{$\sharp$}%
\spacefactor1000 }

\setlength{\textheight}{10in}

\begin{document} 
\name{Royce Dylan Townsend}
\address{
  \begin{tabular}{r l}
    +61405 018 016 & career@roycetownsend.com
  \end{tabular}
}

\begin{resume}                        

  \section{SKILLS}
  \textbf{Programming}:
    Javascript/Typescript, \Csharp, Java (Android), Objective-C (iPhone), HTML, CSS, Clojure(Script)\\
  \textbf{Libraries}:
    React Native, ASP.Net MVC / WEB Api, Entity Framework\\
  \textbf{Enviroment}:
    SQL Server, IIS, Windows Azure,
    Version control using git, github, svn, cvs, mercurial, whatever.\\
  \\
  \textbf{In the past I've solved problems using}:
    Oracle SQL, MySQL, Azure Table Storage/Blob Storage/Queues, a bunch of AWS services, Flutter/Dart, React.js, NHibernate, Gatsby, Ruby (on Rails), ColdFusion, Lucene (full text search), T4 (code generation), \LaTeX (typesetting), jQuery, Angular, Knockout.js, Apache, Bash, Grunt.js, assemble.js,

  \section{EXPERIENCE}
  Private projects and websites for friends. December 2019 - Present
  \begin{itemize}
    \item Gastby / GraphQL for static site generation
    \item Getting comfortable with Typescript
    \item Trying to sty up to date with React and other Javascript libraries
    \item Creating and deploying (to the Play Store) a simple Android app created with Flutter.
    \item Further experiments are on https://github.com/Royce and some are discussed on https://roycetownsend.com/blog
  \end{itemize}

  Freelancing. October 2016 to November 2019
  \begin{itemize}
    \item iPhone/Android app development using React Native, React Native Navigation
    \item Debugging and extending underlying Java and Objective-C libraries used by the ReactNative app
    \item Maintaining and extending a \Csharp\ /ASP.Net MVC app and WebApi connected to SQL Server
    \item Working remotely for startup.
    \item CI using Team City, and Azure Devops
    \item Android app development using Flutter/Dart to make a simple life/score counter
  \end{itemize}

  Travelling Australia; learning; misc.\\
  February 2015 to October 2016
  \begin{itemize}
    \item Exploring functional programming with Clojure and Clojurescript, particularly focussing on building web and iOS applications using React.js and React Native
  \end{itemize}

  Curtin University, Perth.\\
  Senior Developer. October 2014 to January 2015
  \begin{itemize}
    \item Contructed a \Csharp\ /ASP.Net MVC app using: AngularJs and EntityFramework, and integrating with ActiveDirectory and a REST API
  \end{itemize}

  Curtin University, Perth.\\
  Senior Developer. September 2013 to November 2013
  \begin{itemize}
    \item Mentoring, trouble-shooting
    \item Guiding and reviewing the system design/architecture
  \end{itemize}
  \vspace{-0.1in}
  Programmer. October 2006 to September 2013
  \begin{itemize}
    \item Part of the formation of an Agile (Scrum/XP) team
    \item Facilitated retrospectives (review and process improvement)
    \item Built many web applications (\Csharp\ /ASP.Net MVC)
    \item Unit Testing / Test-driven-development with recent attempts at automated testing against user acceptence criteria 
    \item Built and maintain OASIS, a web application
            that has 500+ students logged in at any time. Custom ETL tool to transfer sensitive data from on-premise systems to cloud services (Azure Queues, Table Storage, Blob Storage, worker roles).
    \item Interfacing with Oracle Database and SQL server
    \item Maintaining or rewriting legacy Coldfusion and Java applications
    \item Database schema design (relation databases and NoSQL)
  \end{itemize}
  
  Freelance Programmer. 2007-Present.
  \begin{itemize}
    \item Created a custom client management system (Ruby on Rails)
    \item Created and maintained various websites
  \end{itemize} 
  
  Curtin Volunteers. Bentley, Perth. \\
  Web Team Leader.  June 2006 to Dec 2006.\\
  Director of Technology.  July 2005 to June 2006.
  \begin{itemize}
    \item Developing, designing and maintaining the website (CSS, HTML) and building an administration tool (Coldfusion)
  \end{itemize} 

  \section{EDUCATION}
  Curtin University of Technology, Western Australia. \\
  Bach. Engineering (Software Engineering). 2011.

  \section{REFEREES}
  Matthew Davies, Readify Consultant.
  \hfill $\longleftarrow$ Employer/Client for freelance work\\
  Readify. \\
  matt@mdavies.net  \\
  Mobile: 0433 336 935 \\
  \\
  Robert Moore, Lead Consultant.
  \hfill $\longleftarrow$ Fellow programmer; Former team leader\\
  Readify. \\
  robertmooreweb@gmail.com \\
  Mobile: 0400 777 763 \\
  \\

\end{resume} 

\vfill
\centering

\hspace{-1.75in}  When I am not programming (and am awake) I can be found swing dancing, \\
\hspace{-1.75in}  DJing blues and swing music for dancers, teaching dance, rock-climbing,\\
\hspace{-1.75in}  running D\&D, cycling, running, juggling, fire twirling, playing boardgames,\\
\hspace{-1.75in}  enjoying music, drinking coffee, gardening, or listening to a book.

\vfill
\hspace{-1.75in}  The resume is made with \LaTeX. \\
\hspace{-1.75in}  You can find the source code and a copy of the license
                  at www.github.com/royce/resume.

\end{document}

