\documentclass[a4paper]{letter}

\usepackage[utf8]{inputenc}

\usepackage{a4}

%c C sharp
\def\Csharp{%
    C\raise.60ex\hbox{$\sharp$}%
\spacefactor1000 }

\pagestyle{empty}

\begin{document}
\begin{letter}{}

% \address{37 Clemros Way\\
%         Leeming WA 6149\\[4pt]
%         ABN: 66 364 610 401\\}
\signature{Royce Townsend}

\opening{Hi Allan,}

It is with great joy that I find myself applying for the role of `Developer, CITS - Business Systems' (position number \textbf{3500327}). I fondly remember working at Curtin, and would like to do it again.

\begin{quote}
  ``Are you an enthusiastic, motivated front-end developer who wants to be part of a small agile team?''
\end{quote}

Yes, that's me! I am competent with any part (front-end or back-end) of web applications, but I find more enjoyment in the front-end work. HTML, CSS, Javascript, talking to clients/users about what they want -- I love it!

I am very familiar with the kinds of applications you have at Curtin; built in \Csharp\  using ASP.NET MVC with Nhibernate or Entity Framework (to wrap the database). I am glad to hear that the newer applications have added Angular JS and Web API services. My last professional software project used Angular JS talking to a web API on top of MVC and EF6 app.

I am also comfortable with web applications built using Microsoft Azure, and Coldfusion -- I know CITS has a few of these floating around too.

I have all the `essential' and `desirable' skills/experiences mentioned in the job posting, but I would like to highlight how I fulfil a few in particular:

  \begin{itemize}
    \item At Curtin Uni I used both AngularJs and KnockoutJs and would be happy to continue using them, but I believe ReactJs has a better approach.
    \item I have used automated testing, in conjunction with TDD and agile/Scrum/XP for (just shy of) a decade and think it works well in a team environment.
    \item Git is my favourite version control system. I use it for profession and personal projects, and have taught others how to use it.
    \item I believe that I am a good communicator. My writing tends to be well-structured and concise; I try not to waste other peoples' time. In person, I am perceptive as to whether a client, for example, has understood what is being said by myself or others and I am comfortable explaining technical subjects without using technical jargon.
    \item Team-work. I have worked both as a general programmer / team member and as a senior developer / team lead. I can work alone, when required, but I miss being in a team of smart individuals who I can teach and learn from.
  \end{itemize}

I think I'd be a great fit for this position at Curtin.

\closing{Kind Regards}

\end{letter}
\end{document}